Notes: New gaugings in 3d from three-form

### 2023-06-15 Draft_3dH3.tex
Correction (6.13).
Updated discussion of the zeta family.

These deformations affect the Kaluza-Klein spectrum as follows: the conformal dimension of each physical field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
\begin{equation} \label{eq:confdimshiftchi}
	2\pi n\longrightarrow e^{-2\psi} \left[ 2\pi n + \Big((q_{\rm L}+q_{\rm R})\,\frac{\chi_{1}}{\alpha}+(q_{\rm L}-q_{\rm R})\,\frac{\chi_{2}}{\alpha}+ (\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1} + (\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
\end{equation}
where the $q$ denote the charges under the different ${\rm U}(1)$.

@@

\paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega},\psi)$}
Again in Hopf coordinates:
\begin{equation}
	\begin{split}
		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\,\d z^{2}\\
		&+ \alpha^{2}\Big[\d\theta^{2} + \Delta\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big(e^{\Omega}\cos^{2}(\theta)\,\d\phi_{1}^{2}+\sin^{2}(\theta)\,\d\phi_{2}^{2}\Big)\Big]\\
		&+\d\ts{\theta}^{2} + \Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+e^{\ts{\Omega}}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\Big)\\
		&+\Delta\,e^{2\psi}\,e^{\Omega}\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{2\psi}\,e^{\ts{\Omega}}\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
		&+\Delta\,e^{2\psi}\,e^{\Omega+\ts{\Omega}}\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
		&-2\,\alpha\,\Delta\,e^{2\psi}\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+e^{\Omega}\,\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(e^{\ts{\Omega}}\,\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
		&+\Delta\,e^{2\psi}\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big[\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+e^{\Omega}\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\Big]\\
		&+\Delta\,e^{2\psi}\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big[e^{\ts{\Omega}}\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2}\Big],
	\end{split}
\end{equation}
with the warp factor
\begin{equation}
	\begin{aligned}
	\Delta^{-1} &= \Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\\
	&+e^{2\psi}\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\\
	&+e^{2\psi}\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right).
	\end{aligned}
\end{equation}

@@

%
%\paragraph{SUSY deformation}
%
%%In Hopf coordinates:
%%\begin{equation}
%%	\begin{split}
%%		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
%%		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{\CE{-}(1-e^{2\omega})} d\psi \,, \\
%%		d\sigma &= vol_{\mathbb{CP}^1} \,.
%%	\end{split}
%%\end{equation}
%
%It is convenient to use the Hopf fibration to describe this, we denote by $\phi$ the coordinate on the $S^1$ fibre and by $\xi$ the homogeneous coordinate on $\mathbb{CP}^1$. The round metric on $S^3$ then reads
%\begin{equation}
%	g= \mathrm{d}s^2_{\mathbb{CP}^1} + (\sigma + \mathrm{d}\phi)^2
%\end{equation}
%where 
%\begin{equation}
%		\mathrm{d}s^2_{\mathbb{CP}^1} &= \frac1{(1+|\xi|^2)^2}\mathrm{d}\xi\,\mathrm{ d}\ov{\xi}\\
%		\sigma&=\frac{i}{2(1+|\xi|^2)}(\xi \mathrm{d} \ov{\xi}-\ov{\xi}\mathrm{d}\xi)\\ 
%		vol_{S^3}&=vol_{\mathbb{CP}^1}\wedge \mathrm{d}\psi .
%\end{equation}
%The deformation does not affect $S_+^3$, but it mixes the $S^1$ factor in the internal space with the Hopf fibre of $S_-^3$. It is parametrised by a real number $\Omega$, such that the metric reads
%\begin{equation}
%		\mathrm{d}s^2 &= \alpha^2(\mathrm{d}s^2_{\mathbb{CP}^1}+\kappa^2) + \mathrm{d}s^2_{S_+^3} + e^{-4\Omega}\mathrm{d}\psi^2\\
%		\kappa &= \mathrm{d}\phi + \sigma - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi.
%\end{equation}
% The three form flux gets changed according to the prescription $\d\phi \rightarrow \d\phi -  \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d \psi$ and we find:
%\begin{equation}
%	H_{(3)}=\alpha^2vol_{\mathbb{CP}^1}\wedge (\d\phi - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi) + vol_{S_+^3}.
%\end{equation}
%
%%
%%In spherical coordinates:
%%\begin{equation}
%%	\begin{aligned}
%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+\alpha^{2}\,\d s^2\left(S^{3}_{-}\right) +e^{-2\omega}\,\d\psi^{2}\\
%%		&\quad+2\,\alpha\,e^{-2\omega}\,\sqrt{-1+e^{2\omega}}\left(-\cos^{2}(\theta)\,\d\varphi_{1}+\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi\\[5pt]
%%		&= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+e^{-4\omega}\,\d\psi^{2}\\
%%		&\quad+\alpha^{2}\bigg[\d \theta^2+\cos^{2}(\theta)\left(\d\varphi_{1}-\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}+\sin^{2}(\theta)\left(\d\varphi_{2}+\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}\bigg] ,\\[5pt]
%%		\d s^2\left(S^{3}_{-}\right) &= \d\theta^{2}+\cos^{2}(\theta)\,\d\varphi_{1}^{2}+\sin^{2}(\theta)\,\d\varphi_{2}^{2}.
%%	\end{aligned}
%%\end{equation}
%
%\paragraph{Non-SUSY deformation}
%Here we study a more general deformation depending on three parameters $\Omega$, $\zeta_{1,8}$ and $\zeta_{2,3}$. It is convenient to write down the uplift in terms of the Hopf coordinates on $S_-^3$, while again $S_+^3$ is not deformed.\\
%\noindent For the metric we find
%%\begin{equation}
%%	\begin{aligned}
%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
%%		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
%%		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
%%		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2}.\\[5pt]
%%		\Delta^{-1} &= 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
%%	\end{aligned}
%%\end{equation}
%\begin{equation}

@@

%\end{equation}
%where $\Delta$ is the warp factor
%\begin{equation}

@@

%\end{equation}
%The three-form flux is 
%\begin{equation}

@@

%\end{equation}
%with the two one forms $\kappa_{1,2}$ defined by 
%\begin{equation}
%\begin{split}

@@

%\end{split}
%\end{equation}
%Note that setting $...$ recovers the supersymmetric deformation described earlier.
%%In Hopf coordinates:
%% \begin{equation}
%% \begin{split}
%% ds^2 &= \alpha^2 \left[ d\alpha_1^2 +  ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
%% \kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
%% d\sigma &= vol_{\mathbb{CP}^1} \,.
%% \end{split}
%% \end{equation}
%% \begin{equation}
%% 	\begin{aligned}
%% 		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
%% 		&\quad + \Delta\,\alpha^{2}\bigg[\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm I}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm R}^{2}\Big)\,\d z_{\rm R}^{2}\\
%% 		&\qquad\ \  + \frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm R}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm I}^{2}\Big)\,\d z_{\rm I}^{2}\\
%% 		&\qquad\ \  + 2\,\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(-\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(2+\vert z\vert^{2}\right)+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d z_{\rm R}\d z_{\rm I}\\
%% 		&\qquad\ \  +2\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\,\vert z\vert^{2}+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d\theta^{2}\bigg]\\
%% 		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
%% 		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
%% 		\Delta^{-1} &= 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
%% 	\end{aligned}
%% \end{equation}
%
%%%%%
%
%%\begin{equation}
%%	\begin{aligned}
%%		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
%%		&\quad + \frac{\alpha^{2}}{1+\gamma\,\vert z\vert^{2}}\bigg[\Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm I}^{2}\right)+\left(\gamma-1\right)\,z_{\rm R}^{2}\Big)\,\frac{\d z_{\rm R}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
%%		&\qquad + \Big(\left(1+\vert z\vert^{2}\right)\left(1+z_{\rm R}^{2}\right)+\left(\gamma-1\right)\,z_{\rm I}^{2}\Big)\,\frac{\d z_{\rm I}^{2}}{\left(1+\vert z\vert^{2}\right)^{2}} - 2\,\Big(1+\vert z\vert^{2}-\left(\gamma-1\right)\Big)\,\frac{\d z_{\rm R}\d z_{\rm I}}{\left(1+\vert z\vert^{2}\right)^{2}}\\
%%		&\qquad+2\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\left(\gamma+\vert z\vert^{2}\right)\d\theta^{2}\bigg]\\

>>>>

These deformations affect the Kaluza-Klein spectrum as follows: the conformal dimension of each physical field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
\begin{equation} \label{eq:confdimshiftchi}
	2\pi n\longrightarrow e^{-\psi} \left[ 2\pi n + \frac{1}{2}\Big((q_{\rm L}+q_{\rm R})\,\frac{\chi_{1}}{\alpha}+(q_{\rm L}-q_{\rm R})\,\frac{\chi_{2}}{\alpha}+ (\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1} + (\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big) \right]\,,
\end{equation}
where the $q$ denote the charges under the different ${\rm U}(1)$.

@@

\paragraph{\boldmath $(\zeta,\ts{\zeta},\Omega,\ts{\Omega},\psi)$}
Again in Hopf coordinates:
\begin{equation} \label{eq:metriczeta}
	\begin{split}
		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) -\Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\,\d z^{2}\\
		&+ \alpha^{2}\Big[\d\theta^{2} + \Delta\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big(e^{\Omega}\cos^{2}(\theta)\,\d\phi_{1}^{2}+\sin^{2}(\theta)\,\d\phi_{2}^{2}\Big)\Big]\\
		&+\d\ts{\theta}^{2} + \Delta\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}^{2}+e^{\ts{\Omega}}\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}^{2}\Big)\\
		&+\Delta\,e^{2\psi}\,e^{\Omega}\cos^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{1}\right)^{2}+\Delta\,e^{2\psi}\,e^{\ts{\Omega}}\sin^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{2}\right)^{2}\\
		&+\Delta\,e^{2\psi}\,e^{\Omega+\ts{\Omega}}\cos^{2}(\theta)\sin^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{1}\,\d\phi_{1}-\zeta_{2}\,\d\ts{\phi}_{2}\right)^{2}+\Delta\,e^{2\psi}\,\sin^{2}(\theta)\cos^{2}(\ts{\theta}) \left(\alpha\,\ts{\zeta}_{2}\,\d\phi_{2}-\zeta_{1}\,\d\ts{\phi}_{1}\right)^{2}\\
		&-2\,\alpha\,\Delta\,e^{2\psi}\left(\zeta_{1}\,\cos^{2}(\theta)\,\d\phi_{1}+e^{\Omega}\,\zeta_{2}\,\sin^{2}(\theta)\,\d\phi_{2}\right)\left(e^{\ts{\Omega}}\,\ts{\zeta}_{1}\,\cos^{2}(\ts{\theta})\,\d\ts{\phi}_{1}+\ts{\zeta}_{2}\,\sin^{2}(\ts{\theta})\,\d\ts{\phi}_{2}\right)\\
		&+\Delta\,e^{2\psi}\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\Big[\cos^{2}(\theta)\left(\alpha\,\zeta_{1}\,\d\phi_{1}+\d z\right)^{2}+e^{\Omega}\sin^{2}(\theta)\left(\alpha\,\zeta_{2}\,\d\phi_{2}+\d z\right)^{2}\Big]\\
		&+\Delta\,e^{2\psi}\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big[e^{\ts{\Omega}}\cos^{2}(\ts{\theta})\left(\ts{\zeta}_{1}\,\d\ts{\phi}_{1}-\d z\right)^{2}+\sin^{2}(\ts{\theta})\left(\ts{\zeta}_{2}\,\d\ts{\phi}_{2}-\d z\right)^{2}\Big],
	\end{split}
\end{equation}
with the warp factor
\begin{equation}
	\begin{aligned}
	\Delta^{-1} &= \Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\\
	&+e^{2\psi}\Big(\cos^{2}(\theta)+e^{\Omega}\sin^{2}(\theta)\Big)\left(\ts{\zeta}_{2}^{2}\cos^{2}(\ts{\theta})+e^{\ts{\Omega}}\,\ts{\zeta}_{1}^{2}\sin^{2}(\ts{\theta})\right)\\
	&+e^{2\psi}\Big(e^{\ts{\Omega}}\cos^{2}(\ts{\theta})+\sin^{2}(\ts{\theta})\Big)\left(e^{\Omega}\,\zeta_{2}^{2}\cos^{2}(\theta)+\zeta_{1}^{2}\sin^{2}(\theta)\right).
	\end{aligned}
\end{equation}

@@

As previously, the deformation breaks the isometry group down to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries. Note that for
\begin{equation}
	\zeta_{1}=\pm\zeta_{2},\quad \ts{\zeta}_{1}=\mp\ts{\zeta}_{2}\,\quad\Omega=\ts{\Omega}=0,
\end{equation}
the solution~\eqref{eq:metriczeta} reproduces eq.~\eqref{eq:chipsi} for
\begin{equation}
	\chi_{1}=\pm\chi_{2}=\frac{\zeta_{1}}{1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2}},\quad \ts{\chi}_{1}=\mp\ts{\chi}_{2}=-\frac{\ts{\zeta}_{1}}{1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2}},\quad e^{2\psi}=\frac{1}{(1+\zeta_{1}^{2}+\ts{\zeta}_{1}^{2})^{2}},
\end{equation}
with ${\cal N}=(4,0)$ (or $(0,4)$) and symmetry enhancement to ${\rm SO}(4)\times{\rm U}(1)^{2}$. There seems to be no other points with (super)-symmetry enhancement in the scalar manifold.

% \paragraph{SUSY deformation}

% %In Hopf coordinates:
% %\begin{equation}
% %	\begin{split}
% %		ds^2 &= \alpha^2 \left[ ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
% %		\kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{\CE{-}(1-e^{2\omega})} d\psi \,, \\
% %		d\sigma &= vol_{\mathbb{CP}^1} \,.
% %	\end{split}
% %\end{equation}

% It is convenient to use the Hopf fibration to describe this, we denote by $\phi$ the coordinate on the $S^1$ fibre and by $\xi$ the homogeneous coordinate on $\mathbb{CP}^1$. The round metric on $S^3$ then reads
% \begin{equation}
% 	g= \mathrm{d}s^2_{\mathbb{CP}^1} + (\sigma + \mathrm{d}\phi)^2
% \end{equation}
% where 
% \begin{equation}
% 	\begin{split}
% 		\mathrm{d}s^2_{\mathbb{CP}^1} &= \frac1{(1+|\xi|^2)^2}\mathrm{d}\xi\,\mathrm{ d}\ov{\xi}\\
% 		\sigma&=\frac{i}{2(1+|\xi|^2)}(\xi \mathrm{d} \ov{\xi}-\ov{\xi}\mathrm{d}\xi)\\ 
% 		vol_{S^3}&=vol_{\mathbb{CP}^1}\wedge \mathrm{d}\psi .
% 	\end{split}
% \end{equation}
% The deformation does not affect $S_+^3$, but it mixes the $S^1$ factor in the internal space with the Hopf fibre of $S_-^3$. It is parametrised by a real number $\Omega$, such that the metric reads
% \begin{equation}
% 	\begin{split}
% 		\mathrm{d}s^2 &= \alpha^2(\mathrm{d}s^2_{\mathbb{CP}^1}+\kappa^2) + \mathrm{d}s^2_{S_+^3} + e^{-4\Omega}\mathrm{d}\psi^2\\
% 		\kappa &= \mathrm{d}\phi + \sigma - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi.
% 	\end{split}
% \end{equation}
% The three form flux gets changed according to the prescription $\d\phi \rightarrow \d\phi -  \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d \psi$ and we find:
% \begin{equation}
% 	H_{(3)}=\alpha^2vol_{\mathbb{CP}^1}\wedge (\d\phi - \frac1{\alpha}e^{-2\Omega}\sqrt{e^{2\Omega}-1}\d\psi) + vol_{S_+^3}.
% \end{equation}

% %
% %In spherical coordinates:
% %\begin{equation}
% %	\begin{aligned}
% %		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+\alpha^{2}\,\d s^2\left(S^{3}_{-}\right) +e^{-2\omega}\,\d\psi^{2}\\
% %		&\quad+2\,\alpha\,e^{-2\omega}\,\sqrt{-1+e^{2\omega}}\left(-\cos^{2}(\theta)\,\d\varphi_{1}+\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi\\[5pt]
% %		&= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right)+e^{-4\omega}\,\d\psi^{2}\\
% %		&\quad+\alpha^{2}\bigg[\d \theta^2+\cos^{2}(\theta)\left(\d\varphi_{1}-\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}+\sin^{2}(\theta)\left(\d\varphi_{2}+\frac{e^{-2\omega}}{\alpha}\sqrt{-1+e^{2\omega}}\,\d\psi\right)^{2}\bigg] ,\\[5pt]
% %		\d s^2\left(S^{3}_{-}\right) &= \d\theta^{2}+\cos^{2}(\theta)\,\d\varphi_{1}^{2}+\sin^{2}(\theta)\,\d\varphi_{2}^{2}.
% %	\end{aligned}
% %\end{equation}

% \paragraph{Non-SUSY deformation}
% Here we study a more general deformation depending on three parameters $\Omega$, $\zeta_{1,8}$ and $\zeta_{2,3}$. It is convenient to write down the uplift in terms of the Hopf coordinates on $S_-^3$, while again $S_+^3$ is not deformed.\\
% \noindent For the metric we find
% %\begin{equation}
% %	\begin{aligned}
% %		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
% %		&\quad + \alpha^{2}\left(\d\theta^{2}+\Delta\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\cos^{2}(\theta)\,\d\varphi^{2}_{1}+\Delta\left(2+e^{2\Omega}\,\zeta_{1,8}^{2}\right)\,\sin^{2}(\theta)\,\d\varphi_{2}^{2}\right)\\
% %		&\quad+2\sqrt{2}\,\alpha\,\Delta\left(-\zeta_{2,3}\,\cos^{2}(\theta)\,\d\varphi_{1}+\zeta_{1,8}\,\sin^{2}(\theta)\,\d\varphi_{2}\right)\,\d\psi \\
% %		&\quad+2\,\Delta\left(\cos^{2}(\theta)+e^{2\Omega}\,\sin^{2}(\theta)\right)\,\d\psi^{2}.\\[5pt]
% %		\Delta^{-1} &= 2\,e^{2\Omega}+\zeta_{2,3}^{2}+\cos^{2}(\theta)\left(2-2\,e^{2\Omega}-\zeta_{2,3}^{2}+e^{2\Omega}\,\zeta_{1,8}^{2}\right).
% %	\end{aligned}
% %\end{equation}
% \begin{equation}

@@

% \end{equation}
% where $\Delta$ is the warp factor
% \begin{equation}

@@

% \end{equation}
% The three-form flux is 
% \begin{equation}

@@

% \end{equation}
% with the two one forms $\kappa_{1,2}$ defined by 
% \begin{equation}

@@

% \end{equation}
% Note that setting $...$ recovers the supersymmetric deformation described earlier.
% %In Hopf coordinates:
% % \begin{equation}
% % \begin{split}
% % ds^2 &= \alpha^2 \left[ d\alpha_1^2 +  ds^2_{\mathbb{CP}^1} + \kappa^2 \right] + ds^2_{\tilde{S}^3} + e^{-4\omega} d\psi^2 \,, \\
% % \kappa &= d\theta + \sigma - \frac1{\alpha} e^{-2\omega} \sqrt{1-e^{2\omega}} d\psi \,, \\
% % d\sigma &= vol_{\mathbb{CP}^1} \,.
% % \end{split}
% % \end{equation}
% % \begin{equation}
% % 	\begin{aligned}
% % 		\d s^{2} &= \d s^2\left({\rm AdS}_{3}\right)+\d s^2\left(S^{3}_{+}\right) \\
% % 		&\quad + \Delta\,\alpha^{2}\bigg[\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm I}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm R}^{2}\Big)\,\d z_{\rm R}^{2}\\
% % 		&\qquad\ \  + \frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(1+(2+\vert z\vert^{2})\,z_{\rm R}^{2}\right)+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,z_{\rm I}^{2}\Big)\,\d z_{\rm I}^{2}\\
% % 		&\qquad\ \  + 2\,\frac{1}{\left(1+\vert z\vert^{2}\right)^{2}}\Big(-\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(2+\vert z\vert^{2}\right)+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d z_{\rm R}\d z_{\rm I}\\
% % 		&\qquad\ \  +2\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\d\theta+\Big(\left(2+e^{2\Omega}\zeta_{1,8}^{2}\right)\,\vert z\vert^{2}+2\,e^{2\Omega}+\zeta_{2,3}^{2}\Big)\,\d\theta^{2}\bigg]\\
% % 		&\quad + \Delta\,\alpha\bigg[-2\sqrt{2}\,e^{2\Omega}\,\zeta_{1,8}\,\left(z_{\rm I}\,\d z_{\rm R}-z_{\rm R}\,\d z_{\rm I}\right)\,\d\psi-2\sqrt{2}\left(e^{2\Omega}\,\zeta_{1,8}\,\vert z\vert^{2}+\zeta_{2,3}\right)\,\d\theta\,\d\psi\bigg]\\
% % 		&\quad + 2\,\Delta\left(1+e^{2\Omega}\,\vert z\vert^{2}\right)\,\d\psi^{2} ,\\[5pt]
% % 		\Delta^{-1} &= 2+e^{2\Omega}\zeta_{1,8}^{2}+\left(2\,e^{2\Omega}+\zeta_{2,3}^{2}\right)\,\vert z\vert^{2}.
% % 	\end{aligned}
% % \end{equation}

% %%%%
